Supporting Information : The importance of a complete description of dependence between variables for ecology and related fields

### 2019-05-02 SupportingInformation.Rmd
typo fixed

\textby{Phenological and population data on aphids.}
Data pre-processing for the aphid data was the same as 
that of @Sheppard2016,
but we excluded one of the 11 sites they used in order to only use sites with at least 30 
years data.

>>>>

\textbf{Phenological and population data on aphids.}
Data pre-processing for the aphid data was the same as 
that of @Sheppard2016,
but we excluded one of the 11 sites they used in order to only use sites with at least 30 
years data.
